### 2018-09-04 manuscript/manuscript.Rmd
good

The experiment compares two within-subject levels of letter orientation (canonical or inverted), participants will experience both conditions within a single experimental session with the conditions presented in a mixed order. The method is almost exactly the same as that of Holcombe, Nguyen, & Goodbourn (in press). The only non-trivial difference is that in that experiment the two conditions were presented in separate blocks, whereas here they are mixed. This will allow us to determine whether simply seeing the backwards letters on an individual trial is sufficient to stop left-side prioritization, or whether having repeated successive trials of a particular condition is necessary. This speaks to how automatic the left-side prioritization observed in @holcombe_implied_2017 is.

@@

@@

### Mixture modeling
In a traditional analyses of performance in cued , the dependent variable would simply be accuracy at reporting the cued letter, for the left and for the right stream. However, that simple analysis can conceal differences in the dynamics of target selection from the streams [@vul_temporal_2008]. To address this, we developed mixture modeling [@goodbourn_pseudoextinction:_2015], which accommodates the possibility that in different conditions or with different streams, the latency of selection or temporal variability of selection may vary together with or separately from the rate of success of selecting a letter.

@@

bb<- BayesFactor::ttestBF(leftCanon$efficacy,rightCanon$efficacy)

```

As seen in Figure 1, when the text was canonically oriented, efficacy for the left stream (`r round(mean(leftCanon$efficacy),2)` ± `r round(sd(leftCanon$efficacy),2)` was much higher than for the right stream (`r round(mean(rightCanon$efficacy),2)` ± `r round(sd(rightCanon$efficacy),2)`), but when the text was inverted, efficacy for the left stream (`r round(mean(leftInverted$efficacy),2)` ± `r round(sd(leftInverted$efficacy),2)` was lower than for the right stream (`r round(mean(rightInverted$efficacy),2)` ± `r round(sd(rightInverted$efficacy),2)`)

efficacy was lower for the left stream () than for the right stream ().

@@

my_lm <- lm(Sepal.Width ~ Sepal.Length + Petal.Width + Petal.Length, data = iris)
apa_lm <- apa_print(my_lm)

@@

>>>>

The experiment compares two within-subject levels of letter orientation (canonical or inverted), participants will experience both conditions within a single experimental session with the conditions presented in a mixed order. The method is almost exactly the same as that of [@holcombe_implied_2017]. The only non-trivial difference is that in that experiment the two conditions were presented in separate blocks, whereas here they are mixed. This will allow us to determine whether simply seeing the backwards letters on an individual trial is sufficient to stop left-side prioritization, or whether having repeated successive trials of a particular condition is necessary. This speaks to how automatic the left-side prioritization observed in @holcombe_implied_2017 is.

@@

The letters in both streams were presented at a rate of 10 per second (66 ms presentation and 33 ms interstimulus interval). The two target letters, which were simultaneous, were surrounded by white cue rings of .1 deg thickness and 5 deg diameter. The screen was viewed from a distance of approximately 57 cm.

@@

### Mixture modeling
In a traditional analyses of performance in cued , the dependent variable would simply be accuracy at reporting the cued letter, for the left and for the right stream. However, that simple analysis can conceal differences in the dynamics of target selection from the streams [@vul_temporal_2008]. To address this, we developed mixture modeling [@goodbourn_pseudoextinction2015], which accommodates the possibility that in different conditions or with different streams, the latency of selection or temporal variability of selection may vary together with or separately from the rate of success of selecting a letter.

@@

bb<- BayesFactor::ttestBF(leftCanon$efficacy-rightCanon$efficacy,
                          leftInverted$efficacy-rightInverted$efficacy)
latexReport<- (apa_print(bb)$statistic)[[1]]
```

As seen in Figure 1, when the text was canonically oriented, efficacy for the left stream (`r round(mean(leftCanon$efficacy),2)` ± `r round(sd(leftCanon$efficacy),2)`) was markedly higher than for the right stream (`r round(mean(rightCanon$efficacy),2)` ± `r round(sd(rightCanon$efficacy),2)`), but when the text was inverted, efficacy for the left stream (`r round(mean(leftInverted$efficacy),2)` ± `r round(sd(leftInverted$efficacy),2)`) was lower than for the right stream (`r round(mean(rightInverted$efficacy),2)` ± `r round(sd(rightInverted$efficacy),2)`).

For our primary statistical analyses (as preregistered), we use "left bias" as the dependent variable. Here, there is very strong evidence, `r latexReport`, that the left bias is greater in the canonical condition (`r mean(leftCanon$efficacy - rightCanon$efficacy)`  ± `r sd(leftCanon$efficacy - rightCanon$efficacy)`) than in the inverted condition (`r mean(leftInverted$efficacy - rightInverted$efficacy)`  ± `r sd(leftInverted$efficacy - rightInverted$efficacy)`).

```{r latencyPrecision}
bflLR<- ttestBF(leftCanon$latency,rightCanon$latency)
latexReportBflLR<- (apa_print(bflLR)$statistic)[[1]]
bflLRinvert<- ttestBF(leftInverted$latency,rightInverted$latency)
latexReportBflLRinvert<- (apa_print(bflLRinvert)$statistic)[[1]]

bfl<- ttestBF(leftCanon$latency - rightCanon$latency, leftInverted$latency - rightInverted$latency)
latexReportBfl<- (apa_print(bfl)$statistic)[[1]]
bfp<- ttestBF(leftCanon$precision - rightCanon$precision, leftInverted$precision - rightInverted$precision)
latexReportBfp<- (apa_print(bfp)$statistic)[[1]]
```

The latency and precision were similar in all four conditions (canonical, left = `r round(mean(leftCanon$latency)*100)` ms, right = `r round(mean(rightCanon$latency)*100)` ms; inverted, left = `r round(mean(leftInverted$latency)*100)` ms, right = `r round(mean(rightInverted$latency)*100)` ms) such that the Bayes Factor t-test supported the null hypothesis of no difference between left and right in both the canonical (`r latexReportBflLR`) and inverted conditions (`r latexReportBflLRinvert`).

canonical left stream: `r mean(leftCanon$latency)*100`
`r mean(rightCanon$latency)*100`
inverted left stream: `r mean(leftInverted$latency)*100`
`r mean(rightInverted$latency)*100`

`r latexReportBfl`

leftCanon$latency

@@

@@

Only differences from Experiment 1 are described below.

The letters in both streams were presented at a slightly slower rate than in Experiment 1, at 8 per second (80 ms presentation and 40 ms interstimulus interval).
